---
title: "pnrfr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pnrfr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# library(pnrfr)
```


# Introduction

The R package pnrfr helps to read channel data and meta information from PNRF files. The package requires the installation of [PNRF Reader Toolkit](https://www.hbm.com/en/2475/support-downloads-perception/
), which is windows dependant. Thus, the package is only supported on windows machine.  

# Installation

You can install the PNRFR package using: 

```{r}
devtools::install_github("nandinisa/pnrfr")
```

# Examples

## PNRF read functions

* read_file_meta - Reads the meta data of a PNRF file
* read_channel_data_obs - Reads the total obs in a given channel from a PNRF file
* read_channel_data - Reads the specified channel data from a PNRF file (at a given samplinng rate)
* read_all_channel_data - Reads all available channel data from a PNRF file (at a given samplinng rate)
* read_segment_data - Reads the segment data corresponding to a channel from a PNRF file (at a given samplinng rate)
* save_channel_data.to_csv - Save channel data to csv

## PNRF RMS function

* compute_moving_average - Computes the moving average for a channel in a PNRF file given a moving window
